Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-09 papers/pair-correlation/paper.tex
make curly braces in matplotlib Tested everything on bingley.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-1.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-1.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-2.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-3.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}
